### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step10.tex
Made the aStart code use a heap and push the rest of the presentation

		% Tile groups 
		\draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
		\draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
		\node[align=center] at (0,4.75) {\textbf{Tiles to assign:}};
		\node[align=center] at (4.25,4.75) {$i-1$\\$i$};
		\draw [thick] (5.5,6) -- (3,6) -- (3,3.5) -- (5.5,3.5) -- (5.5,6);
		\node[align=center, above] at (8,6) {Group 1};
		\node[align=center, above] at (12.5,6) {Group 2};

		% tiles
		\node[align=center, rounded corners, draw] at (7,4.75) {9\\12};
		\node[align=center, rounded corners, draw] at (9,4.75) {11\\13};
		\node[align=center, rounded corners, draw] at (11.5,4.75) {13\\9};
		\node[align=center, rounded corners, draw] at (13.5,4.75) {12\\9.2};		
		\draw [thick] (-4,2) -- (18,2);

@@

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {12\\9.2};
		\node[align=center] at (14,-7) {2.0};

		% grid
		\draw [thick] (2,3.5) -- (2,-8);
		\draw  (-.75,1.75) -- (-.75,-8);
		\draw  (-4,1.125) -- (1.25,1.125);

		\node[align=right] at (-1,3.2) {\scriptsize \textbf{Reference}};
		\node[align=right] at (-1,2.5) {\scriptsize \textbf{Protein Chain}};
		\node[align=right] at (-2.5,1.5) {\tiny Chemical Shift};
		\node[align=right] at (.25,1.5) {\tiny Group};
		\node[align=right] at (-2.5,.5) {13.5};
		\node[align=right] at (-2.5,-2) {9.5};
		\node[align=right] at (-2.5,-4.5) {11.4};
		\node[align=right] at (-2.5,-7) {8.8};
		\node[align=right] at (.25,.5) {1};
		\node[align=right] at (.25,-2) {2};
		\node[align=right] at (.25,-4.5) {1};
		\node[align=right] at (.25,-7) {2};

>>>>

		% \draw [thick] (6,6) -- (10,6) -- (10,3.5) -- (6,3.5) -- (6,6);
				% \draw [thick] (14.5,6) -- (10.5,6) -- (10.5,3.5) -- (14.5,3.5) -- (14.5,6);
				\node[align=center] at (-1,6.25) {\textbf{Tiles to assign:}};
				\node[align=center, rounded corners, draw] at (3.25,6.25) {$i-1$\\$i$\\$P_1$\\$P_2$\\Proline};
				% \draw [thick] (5.5,6) -- (3,6) -- (3,3.5) -- (5.5,3.5) -- (5.5,6);
				% \node[align=center, above] at (8,6) {Group 1};
				% \node[align=center, above] at (12.5,6) {Group 2};

				% tiles
				\node[align=center, rounded corners, draw] at (6.25,6.25) {9\\12\\0.935\\ 0.002\\No};
				\node[align=center, rounded corners, draw] at (9,6.25) {11\\13\\0.013\\ 0.001\\No};
				\node[align=center, rounded corners, draw] at (11.75,6.25) {13\\9\\0.003\\ 0.04\\No};
				\node[align=center, rounded corners, draw] at (14.5,6.25) {12\\9.2\\0.000\\ 0.403\\No};	
				\node[align=center, rounded corners, draw] at (17.25,6.25) {--\\--\\0.000\\ 0.000\\Yes};		
				\draw [thick] (-4,2) -- (18,2);

@@

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
		% \node[align=center] at (14,-7) {2.0};

		% right side row 5
		\draw (12.5,-8) -- (12.5,-8.5);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
		\node[align=center] at (14,-9.5) {2.0};

		% grid
		\draw [thick] (2,3.5) -- (2,-10.5);
		\draw  (-.75,1.75) -- (-.75,-10.5);
		\draw  (-4,1.125) -- (1.5,1.125);

		\node[align=right] at (-1,3.2) {\scriptsize \textbf{Reference}};
		\node[align=right] at (-1,2.5) {\scriptsize \textbf{Protein Chain}};
		\node[align=right] at (-2.5,1.5) {\tiny Chemical Shift};
		\node[align=right] at (.5,1.5) {\tiny $P_n$};
		\node[align=right] at (-2.5,.5) {13.5};
		\node[align=right] at (-2.5,-2) {9.5};
		\node[align=right] at (-2.5,-4.5) {11.4};
		\node[align=right] at (-2.5,-7) {-};
		\node[align=right] at (-2.5,-9.5) {8.8};
		\node[align=right] at (.5,.5) {1};
		\node[align=right] at (.5,-2) {2};
		\node[align=right] at (.5,-4.5) {1};
		\node[align=right] at (.5,-7) {Proline};
		\node[align=right] at (.5,-9.5) {2};

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step11.tex
Made the aStart code use a heap and push the rest of the presentation

		%first 
		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
		% \node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

		%right side row 2
		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, draw, fill = green] at (15.5,-2) {12\\9.2};
		\node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

@@

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};
		\draw (15.5,-3) -- (15.5,-3.5);
		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		\node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
		% \node[align=center] at (14,-7) {2.0};

		% right side row 5
		\draw (12.5,-8) -- (12.5,-8.5);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
		\node[align=center] at (14,-9.5) {2.0};

>>>>

		%first 
		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
		% \node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, draw, fill = green] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

		%right side row 2
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, draw] at (15.5,-2) {12\\9.2};
		% \node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

@@

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};
		\draw (15.5,-3) -- (15.5,-3.5);
		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		\node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-7) {---\\---};

		% right side row 5
		\draw (12.5,-8) -- (12.5,-8.5);
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-9.5) {12\\9.2};
		\node[align=center] at (14,-9.5) {2.0};

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step6.tex
Made the aStart code use a heap and push the rest of the presentation

		%first 
		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
		% \node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

		%right side row 2
		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, draw, fill = green] at (15.5,-2) {12\\9.2};
		\node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, draw] at (8.5,-2) {12\\9.2};
		% \node[align=center] at (10,-2) {1.8};

		% left side row 3
		\node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
		\node[align=center] at (10,-4.5) {5.2};
		\draw (8.5,-3) -- (8.5,-3.5);

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};
		\draw (15.5,-3) -- (15.5,-3.5);
		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		\node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
		% \node[align=center] at (14,-7) {2.0};

		% right side row 5
		\draw (12.5,-8) -- (12.5,-8.5);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
		\node[align=center] at (14,-9.5) {2.0};

>>>>

		%first 
		\node[align=center, rounded corners, draw, fill = green] at (7,.5) {9\\12};
		\node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

		%right side row 2
		\node[align=center, rounded corners, draw] at (12.5,-2) {13\\9};
		% \node[align=center] at (14,-2) {1.0};
		\draw (14,-.5) -- (12.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (15.5,-2) {12\\9.2};
		\node[align=center] at (17,-2) {1.8};
		\draw (14,-.5) -- (15.5,-1);

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, draw, fill=orange] at (8.5,-2) {12\\9.2};
		\node[align=center] at (10,-2) {1.8};

		% left side row 3
		% \node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
		% \node[align=center] at (10,-4.5) {5.2};
		% \draw (8.5,-3) -- (8.5,-3.5);

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-4.5) {9\\12};
		\node[align=center] at (14,-4.5) {1.6};
		% \draw (15.5,-3) -- (15.5,-3.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		% \node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		% \draw (12.5,-5.5) -- (12.5,-6);
		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
		% \node[align=center] at (14,-7) {2.0};

		% % right side row 5
		% \draw (12.5,-8) -- (12.5,-8.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
		% \node[align=center] at (14,-9.5) {2.0};

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step7.tex
Made the aStart code use a heap and push the rest of the presentation

		%first 
		\node[align=center, rounded corners, draw, fill = green] at (7,.5) {9\\12};
		\node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

@@

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-4.5) {9\\12};
		\node[align=center] at (14,-4.5) {1.6};
		% \draw (15.5,-3) -- (15.5,-3.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		% \node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		% \draw (12.5,-5.5) -- (12.5,-6);
		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
		% \node[align=center] at (14,-7) {2.0};

>>>>

		%first 
		\node[align=center, rounded corners, draw] at (7,.5) {9\\12};
		% \node[align=center] at (8.5,.5) {1.5};
		\node[align=center, rounded corners, draw] at (14,.5) {11\\13};
		% \node[align=center] at (15.5,.5) {0.5};
		\draw (10.5,2) -- (7,1.5);
		\draw (10.5,2) -- (14,1.5);

@@

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
		\node[align=center] at (14,-4.5) {1.6};
		% \draw (15.5,-3) -- (15.5,-3.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		% \node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
		\node[align=center] at (14,-7) {1.6};

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step8.tex
Made the aStart code use a heap and push the rest of the presentation

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-4.5) {9\\12};
		\node[align=center] at (14,-4.5) {1.6};
		% \draw (15.5,-3) -- (15.5,-3.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		% \node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-7) {---\\---};
		\node[align=center] at (14,-7) {1.6};

		% % right side row 5
		% \draw (12.5,-8) -- (12.5,-8.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
		% \node[align=center] at (14,-9.5) {2.0};

>>>>

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};
		% \draw (15.5,-3) -- (15.5,-3.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		% \node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-7) {---\\---};
		\node[align=center] at (14,-7) {1.6};

		% right side row 5
		\draw (12.5,-8) -- (12.5,-8.5);
		\node[align=center, rounded corners, draw, fill = orange] at (12.5,-9.5) {12\\9.2};
		\node[align=center] at (14,-9.5) {2.0};

### 2015-04-30 Papers_and_Presentations/DUCURS_2015/tilePlacement/step9.tex
Made the aStart code use a heap and push the rest of the presentation

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, draw, fill=orange] at (8.5,-2) {12\\9.2};
		\node[align=center] at (10,-2) {1.8};

		% left side row 3
		% \node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
		% \node[align=center] at (10,-4.5) {5.2};
		% \draw (8.5,-3) -- (8.5,-3.5);

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {1.6};
		% \draw (15.5,-3) -- (15.5,-3.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		% \node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw, fill = green] at (12.5,-7) {---\\---};
		\node[align=center] at (14,-7) {1.6};

>>>>

		% left side row 2
		\draw (7,-.5) -- (5.5,-1);
		\draw (7,-.5) -- (8.5,-1);
		\node[align=center, rounded corners, draw, fill = orange] at (5.5,-2) {13\\9};
		\node[align=center] at (7,-2) {3.0};
		\node[align=center, rounded corners, draw, fill = green] at (8.5,-2) {12\\9.2};
		\node[align=center] at (10,-2) {1.8};

		% left side row 3
		\node[align=center, rounded corners, draw, fill = orange] at (8.5,-4.5) {11\\13};
		\node[align=center] at (10,-4.5) {5.2};
		\draw (8.5,-3) -- (8.5,-3.5);

		% right side row 3
		\draw (12.5,-3) -- (12.5,-3.5);
		\node[align=center, rounded corners, draw] at (12.5,-4.5) {9\\12};
		% \node[align=center] at (14,-4.5) {2.0};

		% \node[align=center] at (14,-4.5) {1.6};
		% \draw (15.5,-3) -- (15.5,-3.5);
		% \node[align=center, rounded corners, draw, fill = orange] at (15.5,-4.5) {9\\12};
		% \node[align=center] at (17,-4.5) {2.6};

		% right side row 4
		\draw (12.5,-5.5) -- (12.5,-6);
		\node[align=center, rounded corners, draw] at (12.5,-7) {---\\---};
		% \node[align=center] at (14,-7) {2.0};
